---
title: "😊 Hello Thursday"
author: "Blair Wang"
format: 
  html:
    embed-resources: true
    toc: true
    theme: flatly
    code-fold: true
---

## Introduction

Hello world something something


## Overview

```{mermaid}
flowchart LR
  x1[📜 CSV file]
  x2[🧹 Cleanup columns]
  x3[💾 Save CSV file]
  x4[🎲 Preview random 10 rows]
  x5[🕵 Look for coinciding text values]
  x6[🧮 Aggregate data]
  x7[📊 Visualise data]
  x1 --> x2
  x2 --> x4
  x2 --> x5
  x2 --> x6
  x6 --> x7
  
  x2 --> x3
```


Blah blah blah

## Running Code

When you click the **Render** _button_ a document will be generated that includes both content and the output of embedded code. You can embed code like this:

You can add options to executable code like this 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## Step 1. Open the CSV file

```{r}
library(readr)
library(dplyr)

x <- read_csv("./datasets/DHA79.20250129T140111.csv")
print(x)
```

## Step 2. Inspect first 10 rows







Now I will do some other stuff!

Yay!

Etc

Etc

```{r}
# Rename columns and then print again
x <- x %>% rename(statistic_label = "Statistic Label")
x <- x %>% rename(age_group = "Age Group")

sampled_data <- sample_n(x, 10)
print(sampled_data)

# Below code was adapted from Microsoft Copilot, 30 Jan. 2025
# Prompt: "How do I only show the following columns:  - column_A - column_C - column_F"
selected_columns <- select(sampled_data, statistic_label, age_group, ISHMT)
print(selected_columns)

```

We have therefore discovered that ISHMT = International shortlist for hospital morbidity tabulation (ISHMT). For more info see [this link here](https://nhwstat.org/methods/hospital-data-definitions).


## Step 3. Inspect random 10 rows

## Step 4. What is ISHMT?


