---
title: "😊 Hello Thursday"
author: "Blair Wang"
format: 
  html:
    embed-resources: true
    toc: true
    theme: flatly
    code-fold: true
---

## Introduction

Hello world something something


## Overview

```{mermaid}
flowchart LR
  x1[📜 CSV file]
  x2[🧹 Cleanup columns]
  x3[💾 Save CSV file]
  x4[🎲 Preview random 10 rows]
  x5[🕵 Look for coinciding text values]
  x6[🧮 Aggregate data]
  x7[📊 Visualise data]
  x1 --> x2
  x2 --> x4
  x2 --> x5
  x2 --> x6
  x6 --> x7
  
  x2 --> x3
```


## Step 1. Load the libraries


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
```

## Step 2. Open the CSV file

Please note that in the code, we carefully identify each of the data types.

```{r}
cso_dha79 <- read_csv("../../datasets/DHA79.20250129T140111.csv", col_types = list (
  `STATISTIC` = col_character(),
  `Statistic Label` = col_character(),
  `TLIST(A1)` = col_integer(),
  `Year` = col_integer(),
  `C02076V02508` = col_character(),
  `Age Group` = col_character(),
  `C02199V02655` = col_character(),
  `Sex` = col_character(),
  `C02855V03433` = col_character(),
  `ISHMT` = col_character(),
  `UNIT` = col_character(),
  `VALUE` = col_integer()
))
print(cso_dha79)
```

## Step 3. Clean up the dataset

In this step, we:

1. Rename the columns, so they are easier to work with programmatically;
2. Select only the columns we need for the purpose of this analysis;
3. Handle NA values

```{r}
# Rename the columns, so they are easier to work with programmatically
cso_dha79 <- cso_dha79 %>% 
  rename(px_type = "Statistic Label") %>%
  rename(calendar_year = "Year") %>%
  rename(age_group = "Age Group") %>%
  rename(medical_sex = "Sex") %>%
  rename(medical_ishmt = "ISHMT") %>%
  rename(num_cases = "VALUE")

# Select only the columns we need for the purpose of this analysis
cso_dha79_selectedcols <- cso_dha79 %>% select(px_type, calendar_year, age_group, medical_ishmt, medical_sex, num_cases)

# Handle NA values
cso_dha79_selectedcols <- cso_dha79_selectedcols %>% mutate(num_cases = replace_na(num_cases, 0))
```

## Step 4. Handle aggregations in the datset

The dataset contains some rows which aggregate the data of other rows (!):

- Where `medical_ishmt` = _"All causes (A00-Z99 (excl. V, W, X & Y ))"_
- Where `medical_ishmt` = _"All causes excluding dialysis daycases (A00-Z99 (excl. Z49.1 & Z49.2, V, W, X & Y)) ))"_
- Where `medical_sex` = _"Both sexes"_
- Where `age_group` = _"All ages"_

These will mess up our own aggregation process, so we will need to handle them.

**Note:** ISHMT = International shortlist for hospital morbidity tabulation (ISHMT). For more info see [this link here](https://nhwstat.org/methods/hospital-data-definitions).

```{r}
cso_dha79_selectedcols <- cso_dha79_selectedcols %>%
  filter(medical_ishmt != "All causes (A00-Z99 (excl. V, W, X & Y ))") %>%
  filter(medical_ishmt != "All causes excluding dialysis daycases (A00-Z99 (excl. Z49.1 & Z49.2, V, W, X & Y)) ))") %>%
  filter(medical_sex != "Both sexes") %>%
  filter(age_group != "All ages")
```

## Step 5. Plot the data using Plotly

::: {.callout-tip}
## gt?

Have a look at the part that starts with `library(gt)`. This is an alternative to `print(data_for_plotly)`.
:::


Prepare the data for plotly:

```{r}
# Data for plotly
data_for_plotly <- cso_dha79_selectedcols %>%
  group_by(age_group, calendar_year) %>%
  summarize(
    total_num_cases = sum(num_cases),
    .groups = "keep"
  ) %>%
  ungroup()

library(gt)
data_for_plotly %>%
  gt() %>%
  fmt_number(
    columns = total_num_cases,
    sep_mark = ",",
    decimals = 0
  ) %>%
  opt_table_font(
    size = "9pt",
    font = list(
      "Courier",
      "monospace"
    )
  )
# print(data_for_plotly)
```


Show the plot:

```{r}
plot <- data_for_plotly %>%
  plot_ly(
    x = ~total_num_cases,
    type = "box",
    name = ~age_group
  )

plot
```
