---
title: "Hello Wednesday :)"
author: "Blair Wang"
format:
  html:
    toc: true
    embed-resources: true
    theme: flatly
    code-fold: true
    code-summary: "What does the code say? 🦊"
---

## Quarto


```{mermaid}
flowchart LR
  x1[📜 CSV file]
  x2[🧹 Cleanup columns]
  x3[💾 Save CSV file]
  x4[🎲 Preview random 10 rows]
  x5[🕵 Look for coinciding text values]
  x6[🧮 Aggregate data]
  x7[📊 Visualise data]
  x1 --> x2
  x2 --> x4
  x2 --> x5
  x2 --> x6
  x6 --> x7
  
  x2 --> x3
```


## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
library(dplyr)
library(readr)

cso_dha79 <- read_csv("datasets/DHA79.20250129T140111.csv", show_col_types = FALSE)

# Rename columns
cso_dha79 <- cso_dha79 %>% rename(age_group = "Age Group")
cso_dha79 <- cso_dha79 %>% rename(tlist_a1 = "TLIST(A1)")
cso_dha79 <- cso_dha79 %>% rename(sex = "Sex")

# Random sample
# random_sample <- cso_dha79 %>% sample_n(10)
# print(random_sample)

```

# Observations

## Observation 1: C02076V02508 is synonymous with age_group

```{r}
# distinct_rows <- cso_dha79 %>% distinct(C02076V02508, age_group)
# print(distinct_rows)

distinct_rows <- cso_dha79 %>% distinct(C02199V02655, sex)
print(distinct_rows)

# Drop unnecessary columns
cso_dha79 <- cso_dha79 %>% select(-C02076V02508)
cso_dha79 <- cso_dha79 %>% select(-C02855V03433)

# FYI - ISHMT = International Shortlist for Hospital Morbidity Tabulation
print(cso_dha79)
```

## Observation 2: Something

## Observation 3: Something else

You can _add_ **options** to executable code like this 

```{r}
first_25_rows <- cso_dha79 %>% slice_head(n = 25)
write_csv(first_25_rows, "outputs/cso_dha79_OUTPUT_n25.csv")
```

The `echo: false` option disables the printing of code (only output is displayed).
